---
title: "Data Analysis: Out of the Lab and into the Streets?"
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: Fabian Dablander
output:
  html_document:
    toc: true
    theme: united
    code_folding: show
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE, eval = TRUE,
  fig.align = 'center', fig.width = 10, fig.height = 7, dpi = 300,
  out.width='100%', out.height='100%'
)
```

<!-- avoid border around images -->
<style>
    img {
        border: 0;
    }
</style>

# Introduction
This document includes the statistical analyses reported in the paper Dablander, F.<sup>&#11089;</sup>, Sachisthal, M.<sup>&#11089;</sup>, & Aron, A. (under review) Out of the Labs and into the Streets? Effects of Climate Protests by Environmental Scientists. *Royal Society Open Science*.

# Data preparation
We prepare the data and then test the above hypotheses.

```{r}
library(brms)
library(dplyr)
library(knitr)
library(tidyr)
library(readr)
library(scales)
library(ggplot2)
library(corrplot)
library(gridExtra)
library(BayesFactor)
library(marginaleffects)
source('helpers.R')

df_text <- read_csv('data/dat_text.csv')
df <- read_csv('data/dat_num_all.csv')
demographics <- read.csv('data/demographics_all.csv')
df <- df %>%
  rename(Submission.id = SESSION_ID) %>% 
  left_join(
    demographics %>%
      rename(political_affiliation = U.s..political.affiliation) %>% 
      select(Submission.id, Age, Sex, political_affiliation),
    by = 'Submission.id'
  ) %>% 
  mutate(
    Protest = case_when(
      grepl('Legal', condition) ~ 'Legal March',
      grepl('CD', condition) ~ 'Civil Disobedience'
    ),
    Protest = factor(Protest, levels = c('Civil Disobedience', 'Legal March')),

    Engagement = case_when(
      grepl('None', condition) ~ 'Control',
      grepl('Endorse', condition) ~ 'Support',
      grepl('Join', condition) ~ 'Engaged'
    ),
    # Engagement = factor(Engagement, levels = c('Engaged', 'Support', 'Control')),
    Engagement = factor(Engagement, levels = c('Control', 'Support', 'Engaged')),

    PolicySupport = as.numeric(PolicySupport),
    ActivistSupport = as.numeric(ActivistSupport),
    ScienceCredibility = as.numeric(ScienceCredibility),
    SourceCredibility = as.numeric(SourceCredibility),
    Radical = as.numeric(Radical),
    Donation = as.numeric(Donation_1),

    PoliticalAffiliation = as.numeric(PoliticalAffiliation)
  ) %>% 
  filter(
    # !(political_affiliation %in% c('CONSENT_REVOKED', 'DATA_EXPIRED')),
    Progress == 100 # Remove 10 people who did not finish the survey
  ) %>% 
  mutate(
    political_affiliation = ifelse(
      PoliticalAffiliation %in% c(1, 2), 'Democrat',
      ifelse(
        PoliticalAffiliation %in% c(4, 5), 'Republican', 'Independent'
      )
    ),
    Politics = factor(political_affiliation, levels = c('Democrat', 'Republican', 'Independent'))
  )

contrasts(df$Protest) <- contr.sum(levels(df$Protest))
contrasts(df$Engagement) <- contr.sum(levels(df$Engagement))
contrasts(df$Politics) <- contr.sum(levels(df$Politics))

nrow(df)
```

We remove those participants that incorrectly answer the attention check question.

```{r}
df$AC_Protest %>% table
df_text$AC_Protest %>% table
```

```{r}
df <- df %>% 
  filter(
    (Protest == 'Civil Disobedience' & AC_Protest == '2') |
    (Protest == 'Legal March'        & AC_Protest == '1')
  )
```

We are left with 2,875 responses.

```{r}
nrow(df)
```

We remove the users that responded incoherently or inappropriately to the open text question about what the article was about. This leaves us with 2,856 responses.

```{r}
df_open <- read.csv('data/openAnswers_coded.csv') %>% filter(Usable == 1)

# Additional check from second coder
df_check <- df_open %>% filter(Check == 1)
remove_responseids <- df_check$ResponseId[-c(4, 6)]
df <- df %>%
  left_join(df_open, by = 'ResponseId') %>% 
  filter(Usable == 1, !(ResponseId %in% remove_responseids))

nrow(df)
```


```{r}
# Prepare sub-set of data for later analyses
df_march <- df %>% 
  filter(Protest == 'Legal March') %>% 
  mutate(Y = Radical)

df_civil <- df %>% 
  filter(Protest == 'Civil Disobedience') %>% 
  mutate(Y = Radical)

df_source <- df %>% 
  filter(!is.na(SourceCredibility)) %>% 
  mutate(
    Y = SourceCredibility,
    Engagement = factor(Engagement, levels = c('Support', 'Engaged'))
  )

contrasts(df_source$Engagement) <- contr.sum(levels(df_source$Engagement))
```


```{r, eval = FALSE, echo = FALSE}
# Select 100 for the lottery.
set.seed(1)
df_lottery <- df[sample(nrow(df), size = 100), ]
write.csv(df_lottery, 'df_lottery.csv', row.names = FALSE)
```

We fit all the models for the model-averaged exploratory analysis.

```{r}
# Not included because it is ~50 MB large
fit_all <- readRDS('models/models_scaled.RDS')

# Not included because it is ~300 MB large
if (file.exists('models/fit_all_averaging_scaled.RDS')) {
  
  # For model-averaging later
  fit_all_averaging <- readRDS('models/fit_all_averaging_scaled.RDS')
  fit_policy <- fit_all_averaging$fit_policy
  fit_activist <- fit_all_averaging$fit_activist
  fit_radical <- fit_all_averaging$fit_radical
  fit_source <- fit_all_averaging$fit_source
  fit_science <- fit_all_averaging$fit_science
  
} else {
  
  set.seed(1)
  fit_policy <- get_logml_all_parallel(
    df %>% mutate(Y = PolicySupport), fit_all,
    iter = 4000, cores = 1, chains = 2
  )
  
  set.seed(1)
  fit_activist <- get_logml_all_parallel(
    df %>% mutate(Y = ActivistSupport), fit_all,
    iter = 4000, cores = 1, chains = 2
  )
  
  set.seed(1)
  fit_radical <- get_logml_all_parallel(
    df %>% mutate(Y = Radical), fit_all,
    iter = 4000, cores = 1, chains = 2
  )
  
  set.seed(1)
  fit_source <- get_logml_all_parallel(
    df_source, fit_all,
    iter = 4000, cores = 1, chains = 2, recompile = TRUE
  )
  
  set.seed(1)
  fit_science <- get_logml_all_parallel(
    df %>% mutate(Y = ScienceCredibility), fit_all,
    iter = 4000, cores = 1, chains = 2
  )
  
  fit_all_averaging <- list(
    'fit_policy' = fit_policy,
    'fit_activist' = fit_activist,
    'fit_radical' = fit_radical,
    'fit_source' = fit_source,
    'fit_science' = fit_science
  )
  
  saveRDS(fit_all_averaging, 'models/fit_all_averaging_scaled.RDS')
}
```

# Confirmatory analysis
## Policy support
```{r}
fit <- fit_policy$fit_updated[[5]]
logmls_policy <- fit_policy$logmls

df_effects_policy <- get_all_predictions(
  fit, 'Policy support', variables = c('Engagement', 'Protest')
)

palette <- c("#E67C73", "#F2A489", "#F6E8A7", "#A3C4D4", "#5D92C7")
p1 <- create_plot(
  df, 'PolicySupport', 'Policy support',
  df_effects = df_effects_policy
)
p1
```

### H1: Effect of protest on policy support
Moderate evidence against effect of protest.

```{r}
h1_bfs <- get_bf_matrix(logmls_policy[c(1, 3)])
h1_bfs
```

### H4: Effect of engagement on policy support
Strong evidence of no effect of engagement on policy support.

```{r}
h4_bfs <- get_bf_matrix(
  c(logmls_policy[c(1, 2)],
    log(get_directed_bf(fit_policy$fit_updated[[2]])) + logmls_policy[2]
  )
)
h4_bfs
```

## Activist support
```{r}
fit <- fit_activist$fit_updated[[5]]
logmls_activist <- fit_activist$logmls

df_effects_activist <- get_all_predictions(
  fit, 'Activist support', variables = c('Engagement', 'Protest')
)

p2 <- create_plot(
  df, 'ActivistSupport',
  'Activist support',
  df_effects = df_effects_activist
)
p2
```

### H2: Effect of protest on activist support
Overwhelming evidence in favour of a difference.

```{r}
h2_bfs <- get_bf_matrix(
  c(logmls_activist[c(1, 3)],
    logmls_activist[3] + log(get_directed_bf(
      fit_activist$fit_updated[[3]], groups = 2,
      type = 'decreasing', pars = 'Protest'
    ))
  )
)
h2_bfs
```

### H5: Effect of engagement on activist support
Strong evidence in favour of no effect, although it's a bit lower compared to the directed hypothesis.

```{r}
h5_bfs <- get_bf_matrix(
  c(logmls_activist[c(1, 2)],
    logmls_activist[2] + log(get_directed_bf(
      fit_activist$fit_updated[[2]]
    ))
  )
)
h5_bfs
```

## Perceived radicalness of protest
```{r}
fit <- fit_radical$fit_updated[[5]]
logmls_radical <- fit_radical$logmls

df_effects_radical <- get_all_predictions(
  fit, 'Perceived radicalness', variables = c('Engagement', 'Protest')
)

p3 <- create_plot(
  df, 'Radical',
  'Perceived radicalness',
  df_effects = df_effects_radical,
  lo = 'Not at all radical', hi = 'Extremely radical'
)
p3
```

### H3: Effect of protest on perceived radicalness
Overwhelming effect of higher perceived radicalness for civil disobedience.

```{r}
h3_bfs <- get_bf_matrix(
  c(logmls_radical[c(1, 3)],
    logmls_radical[3] + log(get_directed_bf(
      fit_radical$fit_updated[[3]], groups = 2,
      type = 'increasing', pars = 'Protest'
    ))
  )
)
h3_bfs
```

### H6: Effect of engagement on perceived radicalness for legal march
Strong evidence evidence in favour of no effect of engagement.

```{r}
h6_test <- get_logml_all(
  df_march,
  list('null' = fit_all[[1]], 'full' = fit_all[[2]])
)

# All marginal likelihoods
logmls_all <- c(
  h6_test$logmls,
  h6_test$logmls[2] + log(get_directed_bf(h6_test$fit_updated$full, type = 'decreasing'))
)

h6_bfs <- get_bf_matrix(logmls_all)
h6_bfs
```

### H7: Effect of engagement on perceived radicalness for civil disobedience
Weak evidence evidence in favour of no effect of engagement.

```{r}
h7_test <- get_logml_all(
  df_civil,
  list('null' = fit_all[[1]], 'full' = fit_all[[2]])
)

# All marginal likelihoods
logmls_all <- c(
  h7_test$logmls,
  h7_test$logmls[2] + log(get_directed_bf(h7_test$fit_updated$full, type = 'decreasing'))
)

h7_bfs <- get_bf_matrix(logmls_all)
h7_bfs
```

## Source credibility
We need to recompile the model because otherwise `marginaleffects` throws an error regarding the different factor levels for engagement being present.

```{r}
# Is small enough to be included, but also quick enough to be estimated once
if (!file.exists('models/fit_source_full_final.RDS')) {
  fit <- brm(
    formula = 'Y ~ Engagement + Protest',
    data = df_source, family = brms::cumulative('probit'),
    prior = c(
      prior(student_t(1, 0, 0.15), class = b),
      prior(student_t(1, 0, 2.5), class = Intercept)
    ), cores = 4, chains = 4, iter = 1000, save_pars = save_pars(all = TRUE)
  )
  
  saveRDS(fit, 'models/fit_source_full_final.RDS')
  
} else {
  fit <- readRDS('models/fit_source_full_final.RDS')
}

df_effects_source <- get_all_predictions(
  fit, 'Source credibility', variables = c('Engagement', 'Protest')
) %>% 
  filter(Engagement != 'Control')

p4 <- create_plot(
  df_source, 'SourceCredibility',
  'Source credibility',
  df_effects = df_effects_source,
  lo = 'Not at all', hi = 'A great deal'
)
p4
```

### H8: Effect of engagement on source credibility
Weak evidence in favour of no effect.

```{r}
logmls_source <- fit_source$logmls
h8_bfs <- get_bf_matrix(logmls_source[c(1, 2)])
h8_bfs
```

## Science credibility
```{r}
fit <- fit_science$fit_updated[[5]]

df_effects_science <- get_all_predictions(
  fit, 'Science credibility', variables = c('Engagement', 'Protest')
)

p5 <- create_plot(
  df, 'ScienceCredibility',
  'Science credibility',
  df_effects = df_effects_science,
  lo = 'Not at all', hi = 'A great deal'
)
p5
```

### H9: Effect of engagement on science credibility
Strong evidence for no effect of engagement. 

```{r}
logmls_science <- fit_science$logmls
h9_bfs <- get_bf_matrix(logmls_science[c(1, 2)])
h9_bfs
```

## Figure 1: Proportions and latent means
```{r, fig.height = 11, fig.width = 10}
ggsave(
  'figures/Figure1.pdf',
  grid.arrange(
    p1, p2, p3, p5, p4,
    layout_matrix = rbind(
      c(1, 1, 2, 2),
      c(3, 3, 4, 4),
      c(NA, 5, 5, NA)
    )
  ),
  width = 11, height = 12
)
```

## Table 1: Summary of confirmatory results
```{r}
hyp_names <- c(
  'H1: No effect of protest form on policy support',
  'H2: Higher activist support for legal march',
  'H3: Higher perceived radicalness for civil disobedience',
  'H4: Higher policy support for scientist joining, then supporting, then for no engagement',
  'H5: Higher activist support for scientist joining, then supporting, then for no engagement',
  'H6: Legal march perceived as least radical when scientists join, then for supporting, then for no engagement',
  'H7: Civil disobedience perceived as least radical when scientists join, then for supporting, then for no engagement',
  'H8: No effect of type of engagement on source credibility',
  'H9: No effect of type of engagement on science credibility'
)
hyp_bfs <- c(
  h1_bfs[1, 2],
  h2_bfs[3, 1],
  h3_bfs[3, 1],
  h4_bfs[3, 1],
  h5_bfs[3, 1],
  h6_bfs[3, 1],
  h7_bfs[3, 1],
  h8_bfs[1, 2],
  h9_bfs[1, 2]
)

kable(
  cbind(hyp_names, round(hyp_bfs, 3)),
  col.names = c('Hypothesis', 'Bayes factor in favour of the hypothesis')
)
```

# Exploratory analysis
Here we show the results across political affiliation and report inclusion Bayes factors.

## Policy support
```{r, fig.height = 8}
df_effects_policy <- get_all_predictions(
  fit_policy$fit_updated[[19]], 'Policy support',
  variables = c('Engagement', 'Protest', 'Politics')
)

p7 <- create_plot(
  df, 'PolicySupport',
  'Policy support',
  'Expand offshore drilling',
  political = TRUE,
  df_effects = df_effects_policy
)
p7

ggsave('figures/FigureS4.pdf', p7, width = 9, height = 7)
```

```{r}
inclusion_bfs_policy_support <- get_inclusion_bayes_factors(fit_policy)

kable(
  log(inclusion_bfs_policy_support),
  col.names = c('Effect', 'Log Inclusion Bayes factor')
)
```

## Activist support
```{r, fig.height = 8}
df_effects_activist <- get_all_predictions(
  fit_activist$fit_updated[[19]], 'Activist support',
  variables = c('Engagement', 'Protest', 'Politics')
)

p8 <- create_plot(
  df, 'ActivistSupport', 'Activist support',
  political = TRUE, df_effects = df_effects_activist
)
p8
ggsave('figures/FigureS5.pdf', p8, width = 9, height = 7)
```

```{r}
inclusion_bfs_activist_support <- get_inclusion_bayes_factors(fit_activist)

kable(
  log(inclusion_bfs_activist_support),
  col.names = c('Effect', 'Log Inclusion Bayes factor')
)
```

## Perceived radicalness
```{r, fig.height = 8}
df_effects_radical <- get_all_predictions(
  fit_radical$fit_updated[[19]], 'Perceived radicalness',
  variables = c('Engagement', 'Protest', 'Politics')
)

p9 <- create_plot(
  df, 'Radical', 'Perceived radicalness', 'of the protest',
  political = TRUE, df_effects = df_effects_radical,
  lo = 'Not at all radical', hi = 'Extremely radical'
)
p9
ggsave('figures/FigureS6.pdf', p9, width = 9, height = 7)
```

```{r}
inclusion_bfs_radical <- get_inclusion_bayes_factors(fit_radical)

kable(
  log(inclusion_bfs_radical),
  col.names = c('Effect', 'Log Inclusion Bayes factor')
)
```

## Source credibility
```{r, fig.height = 8}
# Is small enough to be included, but also quick enough to be estimated once
if (!file.exists('models/fit_source_politics.RDS')) {
  fit_source_full <- brm(
    formula = 'Y ~ Engagement + Protest + Politics',
    data = df_source, family = brms::cumulative('probit'),
    prior = c(
      prior(student_t(1, 0, 0.15), class = b),
      prior(student_t(3, 0, 2.5), class = Intercept)
    ), cores = 4, chains = 4, iter = 2000, save_pars = save_pars(all = TRUE)
  )
  
  saveRDS(fit_source_full, 'models/fit_source_politics.RDS')
  
} else {
  fit_source_full <- readRDS('models/fit_source_politics.RDS')
}

df_effects_source <- get_all_predictions(
  fit_source_full, 'Source credibility',
  variables = c('Engagement', 'Protest', 'Politics')
)

p10 <- create_plot(
  df %>% filter(Engagement != 'Control'),
  'SourceCredibility',
  'Source credibility',
  'Trust Dr. Fraser',
  political = TRUE, lo = 'Not at all', hi = 'A great deal',
  df_effects = df_effects_source
)
  
p10
ggsave('figures/FigureS7.pdf', p10, width = 9, height = 7)
```

```{r}
inclusion_bfs_source <- get_inclusion_bayes_factors(fit_source)

kable(
  log(inclusion_bfs_source),
  col.names = c('Effect', 'Log Inclusion Bayes factor')
)
```

## Science credibility
```{r, fig.height = 8}
df_effects_science <- get_all_predictions(
  fit_science$fit_updated[[19]], 'Science credibility',
  variables = c('Engagement', 'Protest', 'Politics')
)

p11 <- create_plot(
  df, 'ScienceCredibility',
  'Science credibility',
  'Trust environmental scientists',
  political = TRUE, df_effects = df_effects_science,
  lo = 'Not at all', hi = 'A great deal'
)
p11
ggsave('figures/FigureS8.pdf', p11, width = 9, height = 7)
```

```{r}
inclusion_bfs_science <- get_inclusion_bayes_factors(fit_science)

kable(
  log(inclusion_bfs_science),
  col.names = c('Effect', 'Log Inclusion Bayes factor')
)
```

## Donation behaviour
```{r, fig.height = 8}
fit_donation <- anovaBF(
  Donation ~ Protest + Engagement + Politics, data = df,
  rscaleEffects = c('Engagement' = 0.15, 'Protest' = 0.15, 'Politics' = 0.15)
)

if (!file.exists('models/df_effects_donation.csv')) {
  df_preds_donation <- get_df_preds_donation(fit_donation[18], df)
  df_effects_donation <- df_preds_donation %>% 
    group_by(Protest, Engagement, Politics) %>% 
    summarize(
      estimate = mean(ypred),
      conf.low = quantile(ypred, 0.025),
      conf.high = quantile(ypred, 0.975),
    )
  
  write.csv(df_effects_donation, 'models/df_effects_donation.csv', row.names = FALSE)
  
} else {
  df_effects_donation <- read.csv('models/df_effects_donation.csv')
}

df_effects_donation <- df_effects_donation %>% 
  mutate(
    Engagement = ifelse(Engagement == 'Support', 'Endorsed', Engagement),
    Engagement = factor(Engagement, labels = c('Control', 'Endorsed', 'Engaged'))
  )

cols <- c('#08519c', 'gray46', '#a50f15')
pdon <- ggplot(
  df_effects_donation, aes(x = Engagement, y = estimate, color = Politics)) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(width = 0.70), width = 0.50, size = 1
  ) +
  geom_point(size = 3, position = position_dodge(width = 0.70)) +
  theme_minimal() +
  labs(
    x = '',
    y = 'Predicted values',
    title = 'Donations across conditions'
  ) +
  scale_color_manual(values = cols) +
  scale_y_continuous(limits = c(10, 40)) +
  facet_wrap(~ Protest) +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    strip.text = element_text(size = 12),
    panel.grid = element_blank(),
    plot.title = element_text(size = 14, hjust = 0.50)
  ) +
  guides(fill = guide_legend(reverse = TRUE))

pdon
```

```{r, eval = FALSE, echo = FALSE, fig.height = 8}
df_mean <- create_mean(df, 'Donation', political = TRUE)

pdon_emp <- ggplot(df_mean, aes(x = Engagement, y = estimate)) +
    geom_point() +
    geom_errorbar(
        data = df_mean, aes(x = Engagement, ymin = conf.low, ymax = conf.high),
        inherit.aes = FALSE, width = 0.20
    ) +
    scale_y_continuous(limits = c(10, 40)) +
    xlab('') +
    ylab('Value') +
    ggtitle('Donations across conditions') +
    theme_minimal() +
    facet_wrap(~ Protest + political_affiliation) +
    theme(
        legend.position = 'top',
        legend.title = element_blank(),
        strip.text = element_text(size = 12),
        panel.grid = element_blank(),
        plot.title = element_text(size = 14, hjust = 0.50)
    ) +
    guides(fill = guide_legend(reverse = TRUE))

pdon_emp
```

```{r}
inclusion_bfs_donation <- c(
  # Main effects
  get_bf_inclusion_donation(fit_donation, 'Engagement')[1],
  get_bf_inclusion_donation(fit_donation, 'Protest')[1],
  get_bf_inclusion_donation(fit_donation, 'Politics')[1],
  
  # Two-way interaction effects
  get_bf_inclusion_donation(fit_donation, 'Engagement', varname2 = 'Protest')[2],
  get_bf_inclusion_donation(fit_donation, 'Engagement', varname2 = 'Politics')[2],
  get_bf_inclusion_donation(fit_donation, 'Protest', varname2 = 'Politics')[2],
  
  # Tree-way interaction effects
  get_bf_inclusion_donation(fit_donation, 'Engagement')[3]
)

names(inclusion_bfs_donation) <- names(inclusion_bfs_science)

kable(
  log(inclusion_bfs_donation),
  col.names = c('Effect', 'Log Inclusion Bayes factor')
)
```

## Figure 2: Latent means across conditions
```{r, fig.width = 10, fig.height = 10}
set.seed(1)
df_preds <- bind_rows(
  get_all_predictions(fit_policy$fit_updated[[19]], outcome = 'Policy support'),
  get_all_predictions(fit_activist$fit_updated[[19]], outcome = 'Activist support'),
  get_all_predictions(fit_radical$fit_updated[[19]], outcome = 'Perceived radicalness'),
  get_all_predictions(fit_science$fit_updated[[19]], outcome = 'Science credibility'),
  get_all_predictions(fit_source_full, outcome = 'Source credibility'),
  df_effects_donation %>% mutate(outcome = 'Donation')
) %>% 
  mutate(
    Politics = factor(Politics, levels = c('Democrat', 'Independent', 'Republican')),
    outcome = factor(
      outcome,
      levels = c(
        'Policy support', 'Activist support',
        'Perceived radicalness', 'Source credibility',
        'Science credibility', 'Donation'
      )
    ),
    panel = c(rep(1:4, each = 18), rep(5, 12), rep(16, 18))
  )

cols <- c('#08519c', 'gray46', '#a50f15')
ppost <- ggplot(
  df_preds, aes(x = Engagement, y = estimate, col = Politics, shape = Protest)
) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(width = 0.70), width = 0.50, size = 1
  ) +
  geom_point(size = 3, position = position_dodge(width = 0.70)) +
  theme_minimal() +
  labs(
    x = '',
    y = 'Latent mean',
    title = 'Latent means across outcomes and conditions'
  ) +
  scale_color_manual(values = cols) +
  facet_wrap(~ outcome, ncol = 2, scales = 'free_y') +
  theme(
    plot.title = element_text(size = 14, hjust = 0.50),
    strip.text = element_text(size = 10),
    legend.title = element_blank(),
    legend.position = 'top',
    legend.box = 'vertical',
    legend.spacing.y = unit(-0.25, 'cm')
  )

ggsave('figures/Figure2.pdf', ppost, width = 9, height = 9)
ppost
```

## Table 2: Summary of exploratory results
```{r}
varnames <- c(
  'Policy support',
  'Activist support',
  'Perceived radicalness',
  'Source credibility',
  'Science credibility',
  'Donation'
)

inclusion_bfs <- cbind(
  inclusion_bfs_policy_support,
  inclusion_bfs_activist_support,
  inclusion_bfs_radical,
  inclusion_bfs_source,
  inclusion_bfs_science,
  inclusion_bfs_donation
)

format_scientific <- function(x) {
  if (is.numeric(x) && x > 1000) {
    formatted <- formatC(x, format = "e", digits = 2)
    # Replace 'e+' with ' x 10^' for the desired format
    formatted <- gsub("e\\+0*", " x 10^", formatted)
    formatted <- gsub("e\\-", " x 10^-", formatted)
    return(formatted)
  }
  return(as.character(x))
}

colnames(inclusion_bfs) <- varnames
df_inclusion <- data.frame(round(inclusion_bfs, 3)) %>% tibble::rownames_to_column()
colnames(df_inclusion) <- c('Factor', str_replace_all(colnames(df_inclusion)[-1], '\\.', ' '))

# Apply the formatting function to the data frame
df_inclusion[, -1] <- as.data.frame(lapply(df_inclusion[, -1], function(column) {
  sapply(column, format_scientific)
}))

kable(df_inclusion)
```

# Supplementary Analysis
## Sensitivity analysis: Confirmatory results
```{r}
prior_widths <- seq(0.10, 0.50, 0.02) / 2

if (!file.exists('results/sensitivity_confirmatory.RDS')) {
    
  # Policy support
  h1_sens <- run_sensitivity(
    df %>% mutate(Y = PolicySupport),
    list('null' = fit_all[[1]], 'full' = fit_all[[3]]),
    prior_widths
  )
  
  h4_sens <- run_sensitivity(
    df %>% mutate(Y = PolicySupport),
    list('null' = fit_all[[1]], 'full' = fit_all[[2]]),
    prior_widths, includes_ordered = TRUE,
    groups = 3, pars = 'Engagement', type = 'increasing'
  )
  
  # Activist support
  h2_sens <- run_sensitivity(
    df %>% mutate(Y = ActivistSupport),
    list('null' = fit_all[[1]], 'full' = fit_all[[3]]),
    prior_widths
  )
  
  h5_sens <- run_sensitivity(
    df %>% mutate(Y = ActivistSupport),
    list('null' = fit_all[[1]], 'full' = fit_all[[2]]),
    prior_widths,
    includes_ordered = TRUE,
    groups = 3, pars = 'Engagement', type = 'increasing'
  )
  
  # Perceived radicalness
  h3_sens <- run_sensitivity(
    df %>% mutate(Y = Radical),
    list('null' = fit_all[[1]], 'full' = fit_all[[3]]),
    prior_widths
  )
  
  h6_sens <- run_sensitivity(
    df_march,
    list('null' = fit_all[[1]], 'full' = fit_all[[2]]),
    prior_widths,
    groups = 3, pars = 'Engagement', type = 'decreasing'
  )
  
  h7_sens <- run_sensitivity(
    df_civil,
    list('null' = fit_all[[1]], 'full' = fit_all[[2]]),
    prior_widths,
    groups = 3, pars = 'Engagement', type = 'decreasing'
  )
  
  # Source credibility
  h8_sens <- run_sensitivity(
    df_source,
    list('null' = fit_all[[1]], 'full' = fit_all[[2]]),
    prior_widths
  )
  
  # Science credibility
  h9_sens <- run_sensitivity(
    df %>% mutate(Y = ScienceCredibility),
    list('null' = fit_all[[1]], 'full' = fit_all[[2]]),
    prior_widths
  )
  
  sens_all <- list(
    'h1_sens' = h1_sens,
    'h2_sens' = h2_sens,
    'h3_sens' = h3_sens,
    'h4_sens' = h4_sens,
    'h5_sens' = h5_sens,
    'h6_sens' = h6_sens,
    'h7_sens' = h7_sens,
    'h8_sens' = h8_sens,
    'h9_sens' = h9_sens
  )
  
  saveRDS(sens_all, 'results/sensitivity_confirmatory.RDS')
} else {
  sens_all <- readRDS('results/sensitivity_confirmatory.RDS')
}
```

## Figure S2: Sensitivity analysis of confirmatory results
```{r, fig.height = 9}
get_bf01 <- function(bfmat) bfmat[1, 2]
sapply(sens_all$h1_sens, get_bf01)

bfs <- do.call('c', lapply(names(sens_all), function(name) {
  sapply(sens_all[[name]], get_bf01)
}))

df_sens <- data.frame(
  type = rep(paste0('H[', seq(9), ']'), each = length(prior_widths)),
  prior_width = rep(prior_widths, 9),
  bfs = bfs
)

custom_label <- function(x) {
  ifelse(
    abs(x) > 500 | abs(x) < 0.002,
    formatC(x, format = 'e', digits = 1),
    format(x, scientific = FALSE)
  )
}

psens <- ggplot(df_sens, aes(x = prior_width * 2, y = bfs)) +
  geom_line(linewidth = 1) +
  facet_wrap(~ type, scales = 'free_y', labeller = label_parsed) +
  labs(
    y = expression(BF[0*1]),
    x = 'Prior width',
    title = 'Bayes factor sensitivity analysis'
  ) +
  scale_y_continuous(labels = custom_label) +
  theme_minimal() +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    strip.text = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.50)
  )

psens
ggsave('figures/FigureS2.pdf', psens, width = 9, height = 9)
```

## Figure S3: Sensitivity analysis of exploratory results
```{r}
prior_widths <- seq(0.10, 0.50, 0.04) / 2

policy_sens <- run_sensitivity_inclusion(
  df %>% mutate(Y = PolicySupport),
  fit_all,
  prior_widths,
  filename = 'results/policy_sens_incl.RDS'
)

activist_sens <- run_sensitivity_inclusion(
  df %>% mutate(Y = ActivistSupport),
  fit_all,
  prior_widths,
  filename = 'results/activist_sens_incl.RDS'
)

radical_sens <- run_sensitivity_inclusion(
  df %>% mutate(Y = Radical),
  fit_all,
  prior_widths,
  filename = 'results/radical_sens_incl.RDS'
)

science_sens <- run_sensitivity_inclusion(
  df %>% mutate(Y = ScienceCredibility),
  fit_all,
  prior_widths,
  filename = 'results/science_sens_incl.RDS'
)

source_sens <- run_sensitivity_inclusion(
  df %>% mutate(Y = SourceCredibility),
  fit_all,
  prior_widths,
  filename = 'results/source_sens_incl.RDS'
)

# For donation behaviour
donation_sens <- run_sensitivity_inclusion_donation(
  df,
  prior_widths,
  filename = 'results/source_donation_incl.RDS'
)
```

```{r, fig.height = 9}
all_sens <- rbind(
  data.frame(policy_sens) %>% mutate(outcome = 'Policy support'),
  data.frame(activist_sens) %>% mutate(outcome = 'Activist support'),
  data.frame(radical_sens) %>% mutate(outcome = 'Perceived radicalness'),
  data.frame(science_sens) %>% mutate(outcome = 'Science credibility'),
  data.frame(source_sens) %>% mutate(outcome = 'Source credibility'),
  data.frame(donation_sens) %>% mutate(outcome = 'Donation')
)

df_sens_all <- all_sens %>%
  pivot_longer(cols = -c(prior_widths, outcome)) %>% 
  mutate(
    name = gsub('\\.', ' x ', name),
    name = factor(
      name,
      levels = c(
        'Engagement', 'Protest', 'Politics',
        'Engagement x Protest', 'Engagement x Politics',
        'Protest x Politics', 'Engagement x Protest x Politics'
      )
    ),
    outcome = factor(
      outcome,
      levels = c(
        'Policy support', 'Activist support',
        'Perceived radicalness', 'Source credibility',
        'Science credibility', 'Donation'
      )
    )
  )

cols <- c('#D55E00', '#A65628', '#029E73', '#56B4E9', '#0072B2', '#CC79A7')
psens2 <- ggplot(df_sens_all, aes(x = prior_widths * 2, y = log(value), color = outcome)) +
  geom_line(linewidth = 1) +
  facet_wrap(~ name, scales = 'free_y') +
  labs(
    y = expression('Log Inclusion' ~ BF[1*0]),
    x = 'Prior width',
    title = 'Sensitivity analysis for exploratory inclusion Bayes factors'
  ) +
  # scale_y_continuous(labels = custom_label) +
  scale_color_manual(values = cols) +
  theme_minimal() +
  theme(
    legend.position = 'top',
    legend.title = element_blank(),
    strip.text = element_text(size = 12),
    plot.title = element_text(size = 14, hjust = 0.50),
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.box.just = "center"
  ) + 
  guides(colour = guide_legend(nrow = 2))

psens2
ggsave('figures/FigureS3.pdf', psens2, width = 9, height = 9)
```

## Supplementary Figure 9: Correlations between measures
```{r}
df_cors <- df %>% 
  select(
    PolicySupport, ActivistSupport, SourceCredibility, ScienceCredibility,
    Radical, Donation, Gender, Age.x, Income, EducationLevel, PoliticalAffiliation
  ) %>% 
  mutate_all(as.numeric)

cormat <- cor(df_cors, method = 'kendall', use = 'pairwise.complete.obs')
diag(cormat) <- NA
rownames(cormat) <- colnames(cormat) <- c(
  'Policy support', 'Activist support', 'Source credibility', 'Science credibility',
  'Perceived radicalness', 'Donation', 'Gender', 'Age', 'Income', 'Educational level',
  'Political affiliation'
)

pdf('figures/FigureS9.pdf', width = 8, height = 8)
corrplot(
  cormat, method = 'color', number.cex = 0.80,
  addCoef.col = 'black', type = 'upper',
  tl.cex = 0.80, addrect = 20, tl.col = 'black',
  na.label = ' ',
  is.corr = TRUE,
  number.digits = 2, col.lim = c(-0.80, 0.80)
)
dev.off()

corrplot(
  cormat, method = 'color', number.cex = 0.80,
  addCoef.col = 'black', type = 'upper',
  tl.cex = 0.80, addrect = 20, tl.col = 'black',
  na.label = ' ',
  is.corr = TRUE,
  number.digits = 2, col.lim = c(-0.80, 0.80)
)
```

# Session info
```{r}
sessionInfo()
```
